Coursera Practical Machine Learning Assignment - Benjamin Stauch
========================================================
Basics
Ok, here we go. We start by loading the packages we need, setting the working directory and importing the data.
```{r}
library(caret)
library(randomForest)
setwd("E:/Users/Benjamin/Documents/R/Coursera/repo/Practical-Machine-Learning-Course")

training <- read.csv("pml-training.csv")
testing20 <- read.csv('pml-testing.csv')
```

Pre-Processing
As we are given a huge number of predictors (160), we start by removing a few. First, we remove those who are irrelevant to the task at hand.
```{r}
training <- subset(training, select = -c(X, user_name, raw_timestamp_part_1, raw_timestamp_part_2, cvtd_timestamp))
```
Then, we remove variable which have at least 50% missing data.
```{r}
training <- training[, colSums(is.na(training)) <= (19622/2)]
```
Next up, we search for variables with near zero variance and remove those as well. This brings us down to 54 variables.
```{r}
nsv <- nearZeroVar(training, saveMetrics=TRUE)
training <- training[,nsv[, 'nzv']==0]
```

Cross-Validation preparation, building the model and evaluating it
Now we split our data from the training file (the "testing"-file is for the other part of the project) into a training and a testing data set.
```{r}
inTrain <- createDataPartition(y=training$classe, p=0.7, list=FALSE)
trainingF <- training[inTrain,]; testingF <- training[-inTrain,]
```
Having done that, let's build the model! Using random forest produces good results in data like the one given to us here. I limit it to 100 trees, as my PC is quite slow.
```{r}
model <- train(classe ~., method='rf', data=trainingF, ntree=100)
```
We now test the model in the test set and measure its accuracy. 0.99xx is very high, leaving only less than a measly 0.01 out of sample error. Success!
```{r}
pred <- predict(model, testingF)
confusionMatrix(pred, testingF$classe)
```
The high accuracy should lead to an error-free prediction in the 20 test samples.
```{r}
answers <- predict(model,testing20)
answers
```



